---
title: "Covid91 vaccine study Final2020"
author: "Mariahkee"
date: "10/26/2020"
output: html_document
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(forcats)
OldData <-read.csv(file="covid91.csv",header=TRUE)
#recode aids to say covid and then remove the annoying "X" from the dataframe
FinalData <- OldData %>% mutate(infected = recode(infected, aids = "covid", none = "OK" )) %>% select(-one_of("X"))
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

A new  preventative vaccine (covid91) is under test in clinical trials. Given the nature of this vaccine it is suspected that the drug may exhibit different effectiveness across the variety of subpopulations tracked. Consider population subgroups by gender( guys and gals), drug use, and sexual orientation. Write a complete report that separately considers this drug for each subgroup and your recommendations as to whether people in the subgroup should take the vaccine.

In this clinical trial, is the vaccine effective preventing the targeted population from getting covid19

$H_0$: Among the targeted population, the drug has no effect in preventing Covi19.

$H_A$: Among the targetedt population, the drug does have an effect in preventing covid19.

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->
 We will use the cat~cat template
# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

#Descriptive results

#Female report

```{r}
DataF= filter(FinalData, sex== "gal")
barchartGC(~infected + treatment,data=DataF, type="percent", main="Gal")

```


Among the females who contracted covid19, it looks like twice as many took the placebo, therefore it appears that the vaccine does have an effect that prevents females from getting covid19

#Guy Report
```{r}
DataF= filter(FinalData, sex== "guy")
barchartGC(~infected + treatment,data=DataF, type="percent", main="Guy")
```


It appears that the vaccine has a negative effect on the guys since they are more likely to get covid19 if they recieve the vaccine.
#Numerical summary  

```{r}
table1 <- xtabs(~infected + treatment, data=DataF)
rowPerc(table1)
colPerc(table1)
```
```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```

#LGBT Report

```{r}
DataLGBTQ = filter(FinalData,LGBTQ=="gay")
barchartGC(~infected + treatment,data=DataLGBTQ)
barchartGC(~infected + treatment,data=DataLGBTQ, type="percent", main="LGBTQ")

```

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```

From the graph above, it appears that the vaccine has a negative effect on gay population since there is more than 60% of chance for them to get covid19 if they recieve the vaccine.

#Drug users report

```{r}
DrugUser = filter(FinalData,DrugUser=="yes")
barchartGC(~infected + treatment,data=DrugUser)
barchartGC(~infected + treatment,data=DrugUser, type="percent", main="DrugUser")

```

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```

#Numerical summary (gal)

```{r}
table1 <- xtabs(~infected + treatment,data=DataF)
rowPerc(table1)
colPerc(table1)
```
```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
